|

### 2023-04-09 paper.Rmd
Correct the number of people filtered by attention checks
These filtered observations are not recorded by our database so there is no way to tell how many of them rather than checking the rejected people via the Prolific system.

Data collection used a total of `r vi_survey %>% count(unique_lineup_id) %>% nrow()` lineups, and resulted in a total of `r nrow(filter(vi_survey, !attention_check))` evaluations from `r vi_survey %>% count(set, exp) %>% nrow()` participants. Roughly half corresponded to the two models, non-linearity and heteroskedasticiy, and the three collection periods had similar numbers in each. <!-- `r nrow(filter(vi_survey, type == "polynomial", !attention_check))` for the non-linearity model, and `r nrow(filter(vi_survey, type == "heteroskedasticity", !attention_check))` for the heteroskedasticity model. This was done in three collection periods (I, II, III), with `r 160 * 18`, `r 150 * 18` and `r 133 * 18 - nrow(filter(vi_survey, null_lineup, !attention_check))` lineups evaluated by 160, 150 and 133 participants, respectively.--> Each participant received two of the `r vi_survey %>% filter(attention_check) %>% count(unique_lineup_id) %>% nrow()` attention check lineups which were used to filter results of participants who were clearly not making an honest effort (only `r vi_survey %>% filter(attention_check, !detect) %>% count(exp, set) %>% nrow()` of `r vi_survey %>% count(set, exp) %>% nrow()`). To estimate $\alpha$ for calculating statistical significance (see Section \ref{sig}) there were `r nrow(filter(vi_survey, null_lineup, !attention_check))` evaluations of `r vi_survey %>% filter(null_lineup, !attention_check) %>% count(unique_lineup_id) %>% nrow()` null lineups. Neither the attention checks nor null lineups were used for the subsequent analysis. The de-identified data, `vi_survey`,  is made available in the R package, `visage`.

The data was collected on lineups constructed from four different fitted value distributions: uniform, normal, skewed and discrete. More data was collected on the uniform (each evaluated by 11 participants) than the others (each evaluated by 5 participants). The analysis in Sections \ref{power-analysis}-\ref{hetero-analysis}, uses only results from lineups generated with uniform fitted values, a total <!--of `r length(unique(pull(filter(vi_survey, !attention_check, !null_lineup, x_dist == "uniform"), unique_lineup_id)))` lineups and--> `r nrow(filter(vi_survey, !attention_check, !null_lineup, x_dist == "uniform"))` lineup evaluations. This was decided in order to compare the conventional and visual test performance for an optimal scenario. Section \ref{effect-of-fitted-value-distributions} examines how the results may be affected if the fitted value distribution was different.

>>>>

Data collection used a total of `r filter(vi_survey, !attention_check) %>% count(unique_lineup_id) %>% nrow()` lineups, and resulted in a total of `r nrow(filter(vi_survey, !attention_check))` evaluations from `r vi_survey %>% count(set, exp) %>% nrow()` participants. Roughly half corresponded to the two models, non-linearity and heteroskedasticiy, and the three collection periods had similar numbers in each. Each participant received two of the `r vi_survey %>% filter(attention_check) %>% count(unique_lineup_id) %>% nrow()` attention check lineups which were used to filter results of participants who were clearly not making an honest effort (only 11 of `r vi_survey %>% count(set, exp) %>% nrow() + 11`). To estimate $\alpha$ for calculating statistical significance (see Section \ref{sig}) there were `r nrow(filter(vi_survey, null_lineup, !attention_check))` evaluations of `r vi_survey %>% filter(null_lineup, !attention_check) %>% count(unique_lineup_id) %>% nrow()` null lineups. Neither the attention checks nor null lineups were used for the subsequent analysis. The de-identified data, `vi_survey`, is made available in the R package, `visage`.

The data was collected on lineups constructed from four different fitted value distributions: uniform, normal, skewed and discrete. More data was collected on the uniform (each evaluated by 11 participants) than the others (each evaluated by 5 participants). The analysis in Sections \ref{power-analysis}-\ref{hetero-analysis}, uses only results from lineups generated with uniform fitted values, a total `r nrow(filter(vi_survey, !attention_check, !null_lineup, x_dist == "uniform"))` lineup evaluations. This was decided in order to compare the conventional and visual test performance for an optimal scenario. Section \ref{effect-of-fitted-value-distributions} examines how the results may be affected if the fitted value distribution was different.
